\section{Liverpool Visit}
\label{section.UoL_visit}

\subsection{Potential Opportunities}
\subsubsection{Collaboration with Liverpool Supervisors}
Although most students will have a supervisor from Liverpool on their team, each project may be different, and you may not have frequent interactions with them before going to Liverpool. This infrequency could be due to various reasons, not necessarily because your work is in a different field. So if you think it would be interesting to collaborate with them in Liverpool, please prepare in advance.

If you haven't had much interaction with them before, make sure to establish some familiarity through some means, which will make future collaboration smoother. This can be through video meetings or emails sharing your research progress and plans, co-authoring papers, or brainstorming potential collaborative research content in advance.

We know that teamwork can happen for different reasons (see \ref{subsection.teamwork}), but in any case, be sure to confirm at least the general direction of your activities during your visit with your Liverpool supervisor in advance, including but not limited to: things that require their involvement, schedule, things you need to prepare, and things you plan to do.

\subsection{Accommodation and Living}
\href{https://hallslife.liverpool.ac.uk}{Halls Life} is the community hub for student accommodation at the University of Liverpool, providing various suggestions on accommodation and living. It is strongly recommended to browse it before departing for the UK, as it can help decide whether to bring certain luggage.

\subsubsection{Visiting Other University Libraries}
When you are traveling and visiting various universities in the UK, if you happen to pass by a university library when you are tired, you can actually go in and sit down, as long as you have applied for \href{https://access.sconul.ac.uk/sconul-access}{SCONUL Access} in advance.

Although different libraries have different policies, in most cases, you can at least enter the library after successfully applying, and some libraries may also provide computer access or book borrowing privileges.

\begin{quote}
    Q. Do I need to complete an online application for each institution I would like to visit?
    
    A. No, although you do need to indicate a library you are interested in visiting as part of your application, your approval email allows you to visit any of those libraries on the list. You do not need to reapply. \hfill 21 Oct, 2024 from \href{https://access.sconul.ac.uk/page/access-faq#Multiple%20applications}{Access FAQ | SCONUL}
\end{quote}

After submitting the application, it will be processed by the University of Liverpool Library, and once approved, you can go to the front desk of each university library with the email to get a visitor card.

\subsection{Food and Entertainment}
\href{https://hallslife.liverpool.ac.uk}{Halls Life} is the community hub for student accommodation at the University of Liverpool, providing various suggestions on food and entertainment.

\begin{flushright}
    October 21, 2022 by \Shiyao

    Translated by GPT
\end{flushright}
