\chapter{Preface}
\thispagestyle{empty}
When I previously communicated with some PhD students, some of them were about to graduate, yet they didn't know they could get office supplies, and some didn't even know where the school gym was, let alone the free fitness room and court resources. Additionally, in the PhD student WeChat group, every year there are people who only find out about the meeting record requirement when it's time for their first APR. Furthermore, even fewer people know about the vast digital resources available under the Liverpool account. Some important things are unknown to oneself, the supervisor, and the office mates, and it might only be discovered upon graduation.

This is the purpose of initiating this guide project. Although every student receives a PGRS Handbook from the school upon enrollment, unfortunately, it is far from enough. Firstly, it lacks a lot of content, such as the Liverpool meeting record and the benefits of the Liverpool account are hardly introduced; secondly, since it is entirely in English, many students, like me, lose interest in reading it after flipping through a few pages of dry content; thirdly, a large pile of materials is distributed upon enrollment, and although the official handbook is important, it can easily get lost in that pile of materials.

For me personally, I also gained a lot of necessary knowledge with the help of senior students in the office when I enrolled. Therefore, I thought of overcoming the shortcomings of the original handbook and recording these experiences to benefit future students. For me, it is also a small contribution to the XJTLU community. I also hope that students who benefit from this handbook can record their valuable experiences during their studies and pass on the help.

This handbook does not intend to replace the PGRS Handbook but serves as a supplement and highlights. Therefore, I hope that students who see this book will still pick up the official handbook from the trash can when they have time, as there may be important discoveries.

If you want to express your gratitude to the authors, you can give a star to this project on GitHub (link: \url{https://github.com/xp-pgrs-unofficial-guide/xp_pgrs_unofficial_guide}). At the same time, if you have been helped by this document, you are encouraged to spend a few minutes recording your personal experiences and passing on the help. For how to contribute, please see Chapter \ref{chapter.author-ins} Writing Guide.

Finally, this handbook is entirely powered by love, without any funding or official background. There may be errors and omissions, please forgive and correct them.

\begin{flushright}
Project Initiator \KW \\
August 18, 2022 at MB \\
Translated by GPT
\end{flushright}


